\documentclass[]{Kushagra-build}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Kushagra Mehta}
\\
\fontspec[Path = fonts/Inconsolata/, Scale=1.5 ]{Inconsolata-SemiBold}\selectfont WEB DEVELOPER \normalfont

\vspace{2em}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.29\textwidth} 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Link
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \linksection{
\faEnvelope \href{mailto:kushagramehta2000@gmail.com}{   kushagramehta2000@gmail.com}\\
\faGithub \href{https://github.com/KushagraMehta}{  @KushagraMehta}\\
\faLinkedinSquare \href{https://www.linkedin.com/in/kushagra-mehta-/}{  Kushagra Mehta} \\
\faPhone \href{tel:+91-9829403414}{ +91-9829403414}\\
\faTwitter \href{https://twitter.com/kushagra_mehta}{   kushagra-mehta} \\
\faPencil \href{https://dev.to/kushagra_mehta}{ Blog}

% }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\subsection{Swami Keshvanand Institute of Technology}
\descript{Bachelor of Science}
Computer Science \\
07/2017 - 07/2021 \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
% \subsection{Programming}
\location{Languages:}
Golang, JavaScript, C++\\ 

\location{Frameworks:}
React \\

\location{Cloud Service:}
AWS, Heroku, Firebase \\
\location{Databases:}
MongoDB, PostgrSQL \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certificates
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Certificates}
\href{https://rhtapps.redhat.com/certifications/badge/verify/JBADVLBCAISWJFM6KOGIYCQ6PYAEQU3CUPSQX2KSDXT6RW46LQ3T7ULZ55KZZ56SKO7EQ3ETTLYZQ4U5NQYTCNA62RUWOCM34WWBUYQ=}{Red Hat certified System Administrator} \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certificates
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Interests}
    \href{https://dev.to/kushagra_mehta}{Blogging} \\
    Competitive online gaming \\
    Badminton \\
    Reading Manga \\
    Cooking \\
\sectionsep

\section{BLogs}

* \href{https://dev.to/kushagra_mehta/webrtc-build-yet-another-chatting-app-but-p2p-e2ee-1l7j}{\underline{WebRTC + Build Chatting app}}
\href{https://dev.to/kushagra_mehta/webrtc-build-yet-another-chatting-app-but-p2p-e2ee-1l7j}{\underline{with P2P/E2EE\faLink}} \\
\vspace{0.8em}
* \href{https://dev.to/kushagra_mehta/series/12260}{\underline{From Zero to Hero in}} \\
\href{https://dev.to/kushagra_mehta/series/12260}{\underline{Authentication\faLink}} \\
\vspace{0.8em}
* \href{https://dev.to/kushagra_mehta/rest-server-with-go-in-5-minutes-3n8l}{\underline{REST server with Go\faLink}}\\
\vspace{0.8em}
* \href{https://dev.to/kushagra_mehta/postgresql-with-go-in-2021-3dfg}{\underline{PostgreSQL with Go in 2021\faLink}} \\
\vspace{0.8em}



\sectionsep
\DTMsetdatestyle{mylastupdate}
\DTMdisplaydate{\the\year}{\the\month}{\the\day}{-1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.70\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\workplace{Marktine}{04/2020 - 06/2020}\\
\position{Front-end Dev.}{Jaipur, IND}
% \begin{tightemize}
\vspace{0.7em} 
\descriptright{\emph{ReactJs, Redux-Saga, CSS JWT, Docker}}
\vspace{1em}
\begin{tightenumerate}
    \item Planned website development, by converting mock-ups into re-usable component with React.
    \item Built and styled new websites by converting their static site to SPA.
    \item Developed new infrastructure based on REST API to provide dynamic on-demand content.
    \item Attained a better secure authentication process by introducing JWT authentication.
    \item Strengthened website by removing multiple third-party packages to introduce consistence and reducing bugs.
    \item Employed new coding practices based on commonly accepted standards for better development and project handling.
    \item Assisted in project production building and web hosting in Docker.
\end{tightenumerate}
\sectionsep

\workplace{AdHoc Networks}{04/2019 - 07/2019} \\
\position{Student Intern}{Jaipur, IND}
\vspace{0.7em} 
\descriptright{\textit{Python, Linux, AWS, Redhat, Django}}
% \vspace{1em} 
\begin{tightenumerate}
    \item As an intern, my priority was to coordinate with new undergraduate students, identify their problems, and establish study plans according to their needs.
    \item Contributed to test creation, doubt session for Student training.
    \item Interacted with a student by phone, email, or in-person to advise on Python, Machine Learning, and Linux.
    \item Maximized productivity by figuring out the key problems and then implemented a repo-checker by which mentors track student's activity on GitHub and guides them accordingly.
    \item By repo-checker, we get positive feedback from students which encouraged them to contribute more to open-source.
\end{tightenumerate}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

\runsubsection{Blog Server}
\descriptright{\href{https://github.com/KushagraMehta/Example-Blog-Server}{\underline{Project on Github\faLink}}}

\descript{GoLang, REST API, PostgreSQL, Docker}
\vspace{0.5em}

A Backend server that provides functionality for user authentication and post-management. Users are able to register themself and post new content and able to like, view, comment on a pre-existing post created by other users. Platform provides searchable option for top posts by tags or by top post-over-all.
\sectionsep

\runsubsection{My Reads}
\descriptright{{\href{https://github.com/KushagraMehta/reactnd-project-myreads-starter}{\underline{Project on Github\faLink}}}}

\descript{JavaScript, ReactJS, REST API, Fetch}
\vspace{0.5em}
My Reads App helps users to organize their bookshelves. Users are able add, remove, or change books from the shelf. They are able to add new books to their shelf. Project in developed using Reactjs.
\sectionsep

\runsubsection{Repo Checker}
\descriptright{\href{https://github.com/KushagraMehta/Repo-Checker}{\underline{Project on Github\faLink}}}
\descript{Python, Django, Github API, CSS3, CanvasJS}
\vspace{0.5em}
 A project using the Django framework where the details are fetched using GitHub API. It has an interactive dashboard with a daily statistical report of the activity done by the user.
\sectionsep

% \project{12345}{ascas}
% \begin{center}
% \runsubsection{{\href{https://gist.github.com/KushagraMehta/70d0553b335d025c4e519df76a065e14#file-project-md}{\achievement{\underline{More Projects\faLink}}}}}
% \end{center}
\sectionsep
\end{minipage} 
\end{document}  


